{\LARGE On the Use of Generic Types for Smart Contracts}

### 2022-05-02 cluster_computing/000_answers_to_reviews.tex

\maketitle

Dear Editor,

\vspace{2mm}

we would like to submit a new version of our paper ``On the Use of Generic Types for Smart Contracts''. We thank you and the reviewers for the comments to our submission. In particular, in this revised manuscript, we have carefully considered the reviewer comments and we have provided a detailed answer to their comments in what follows.

@@

\BOX{
Thank you for your submission. I highly advice you to explain a little bit more about the attack surfaces.
}

We have expanded the Conclusion section with the following paragraph:
``This paper has shown the attack surface due to redefinition of methods with a generic parameter. But another example is the use of instrumented methods to allow access to private state from inner classes: since inner classes are compiled into distinct
bytecode classes, the compiler adds non-private accessors to the private state. These accessors cannot be used at source level, but can be called at bytecode level to gain access to private state.
This paper does not provide a solution to this other issue, but this further example
makes it clear that the attack surface is larger than what described here.''

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5mm}
\hrule
\section*{\textbf{Reviewer 3}}

\BOX{
This manuscript presents a real security issue that the authors found while using generics for writing smart contracts that implement shared entities for the Hotmoka blockchain, and they proposed a possible solution based on an appropriate code rewriting.

There are many major comments in here. I bring as much as I can.
}

@@

\BOX{
3 -- The introduction should be rewritten to clarify its message. Drawbacks of former proposals should be clearly indicated and innovations and new ideas highlighted.
}

We have reorganized the introduction and placed the following sentence at its beginning, to clarify the message. Note that there are no former proposals, since generics have not been used to write smart contracts up to now, to be best of our knowledge. This is expressed clearly now:
``The rules of blockchain transactions are specified by \emph{smart contracts},
that are code written in a variety of programming languages. To the best of our knowledge, none of them allows generic types and, in any case,
nothing has been published about the opportunity but also the risks of using generic types for writing smart contracts.
The contribution of this paper is exactly to show a real-life
use of generic types for an actual smart contract contained in the support
library of the Takamaka language,
and to demonstrate that a naive use
of Java generics can lead to a code security vulnerability that
allows an attacker to earn money by exploiting someone else's work, with both economical and legal side effects.
This paper provides a fix to that specific issue,
by proposing a re-engineering of the code that forces the compiler to generate defensive checks.
More generally, this paper can be useful for the definition of
future bytecode languages for smart contract languages, by
learning from the weaknesses of Java bytecode, in particular from those related to the
compilation of generics.''

\BOX{
4 -- Problem statement, objective \& contribution are not clear.
}

The same change to the introduction highlighted at point 3 above clarifies statement, objective and contribution of the paper now.

@@

\BOX{6 -- For explaining the related work, the authors need to simply mentions their strategy in generic types or smart contracts, mention the advantages and disadvantages. I did not get the general view of the methods or solutions based the explanation that the authors have provided in this part. \\

\noindent 7 -- In my view, the literature survey of introduction is quite weak, unfocused and insufficient. The literature review needs to have a flow that leads to the objectives. What is the essential problem of this work? The authors should really explain the drawback of approaches in the related works especially instead of simply stating what they have done. Besides, please explain the main contribution related to previous approaches or solutions.\\

\noindent 8 -- Section "Related Work" make sure you (i.e., the authors) discuss and cite the most relevant works.}

All these comments about the related work section have pushed us to add a paragraph at its beginning, that clarifies that we have really nothing to compare with directly and we can only put our paper in the context of engineering techniques for strengthening the correctness of software. The new section now starts as follows: ``Programming languages specific to smart contracts (such as Solidity) do not have generic types. General-purpose programming languages do have generic types in most cases, but are much less frequently used for writing smart contracts. In any case, we are not aware of any scientific work on the use of generic types for writing more generic smart contracts, nor of any study on the security risks, and their solutions, that this implies for the resulting smart contracts. From this point of view, the present paper has no direct literature to compare with. It is possible instead to insert this paper in the broader context of software correctness and security. Namely...''.

### 2022-05-02 cluster_computing/050_related_work.tex
Corrected typos

\todo{The solution proposed in this paper could be implemented through an automatic bytecode rectification mechanism. Indeed, the additional method with a more restrictive signature could be automatically added in the bytecode without the need for an explicit method redefinition at the source code level.}

@@

\todo{As regards to this last solution which is based on the definition of new programming languages specific for safe smart contracts writing, the proposed solution could guide a more sophisticated and consious bytecode generation. Indeed, the next generation of programming language for smart contracts should take in mind that the generated bytecode should be called directly, without passing from the source code and the compiler checks. Therefore, any checks which are possible at source code level compilation, like type checking, should remain possible also during bytecode execution.}

>>>>

The solution proposed in this paper could be implemented through an automatic bytecode rectification mechanism. Indeed, the additional method with a more restrictive signature could be automatically added in the bytecode without the need for an explicit method redefinition at the source code level.

@@

As regards to this last solution, which is based on the
definition of new programming languages specific for writing
safe smart contracts, the proposed solution could guide
a more sophisticated and conscious bytecode generation.
Indeed, the next generation of programming languages for smart contracts
should take in mind that the generated bytecode should be called directly,
without passing from the source code and the compiler checks.
Therefore, any checks that are possible at source-code level,
such as type checking, should remain possible also during bytecode execution.
